Logistic Regression Project

In this project we will be working with the UCI adult dataset. We will be attempting to predict if people in the data set belong in a certain class by salary, either making <=50k or >50k per year.

Get the Data
```{r}
library(readr)
a<-read.csv('adult_sal.csv')
```

```{r}
head(a)
```


```{r Getting the structure of the data set}
str(a)

```
```{r Getting summary details}
summary(a)
```

Data Cleaning process
''type_employe column''
```{r Checking the frequency of the column}
table(a$type_employer)

```
```{r combine into a group}
unemp <- function(x)
{
  x <- as.character(x)
  if(x=='Never-worked'|x=='Without-pay')
  {
    return('Unemployed')
  }else{
    return(x)
  }
}
```

```{r apply function in the type_employer}
a$type_employer<-sapply(a$type_employer,unemp)
```

```{r grouped never worked and unemployed}
table(a$type_employer)
```


```{r group the state and local-gov job into SL-gov and self-emp-inc to self-emp}
group_emp <- function(job){
    if (job=='Local-gov' | job=='State-gov'){
        return('SL-gov')
    }else if (job=='Self-emp-inc' | job=='Self-emp-not-inc'){
        return('self-emp')
    }else{
        return(job)
    }
}
```

```{r apply function to the type_employer}
a$type_employer<-sapply(a$type_employer,group_emp)
```

```{r}
table(a$type_employer)
```
'Martial column'
```{r checking the martial column}
table(a$marital)

```
```{r grouping the martial column}
group_marital <- function(mar){
    mar <- as.character(mar)
    
    # Not-Married
    if (mar=='Separated' | mar=='Divorced' | mar=='Widowed'){
        return('Not-Married')
    
    # Never-Married   
    }else if(mar=='Never-married'){
        return(mar)
    
     #Married
    }else{
        return('Married')
    }
}
```

```{r apply fun}
a$marital<-sapply(a$marital,group_marital)
```

```{r display grouped column}
table(a$marital)

```
country column
```{r head of country column}
table(a$country)

```

```{r}
levels(a$country)

```

```{r groupinig as continent}
asia <- c('China','Hong','India','Iran','Cambodia','Japan', 'Laos' ,
          'Philippines' ,'Vietnam' ,'Taiwan', 'Thailand')

north.America <- c('Canada','United-States','Puerto-Rico' )

europe <- c('England' ,'France', 'Germany' ,'Greece','Holand-Netherlands','Hungary',
            'Ireland','Italy','Poland','Portugal','Scotland','Yugoslavia')

latin.and.South.America <- c('Columbia','Cuba','Dominican-Republic','Ecuador',
                             'El-Salvador','Guatemala','Haiti','Honduras',
                             'Mexico','Nicaragua','Outlying-US(Guam-USVI-etc)','Peru',
                            'Jamaica','Trinadad&Tobago')
other <- c('South')
```


```{r grouping everything in group_country}
group_country <- function(cry){
    if (cry %in% asia){
        return('Asia')
    }else if (cry %in% north.America){
        return('North.America')
    }else if (cry %in% europe){
        return('Europe')
    }else if (cry %in% latin.and.South.America){
        return('Latin.and.South.America')
    }else{
        return('Other')      
    }
}
```

```{r apply the function}
a$country <- sapply(a$country,group_country)
```

```{r table of the country}
table(a$country)
```
```{r str of dataset}
str(a)

```
```{r converting into factors}
a$type_employer <- sapply(a$type_employer,factor)
a$country <- sapply(a$country,factor)
a$marital <- sapply(a$marital,factor)
a$income <- sapply(a$income,factor)

```

```{r}
str(a)
```
Missing data
```{r installing amelia package}
library(Amelia)

```

```{r creating ? column as NA  }
a[a=='?'] <- NA
```

```{r viewing the table}
table(a$type_employer)
```
```{r converting into factors}
a$type_employer <- sapply(a$type_employer,factor)
a$marital <- sapply(a$marital,factor)
a$country <- sapply(a$country,factor)
a$occupation <- sapply(a$occupation,factor)
```

```{r}
missmap(a)
```

```{r}
missmap(a,y.at=c(1),y.labels = c(''),col=c('yellow','black'))
```
 EDA 
```{r}
str(a)
```
 
```{r}
library(ggplot2)
library(dplyr)
```


```{r}
ggplot(a,aes(age))+geom_histogram(aes(fill=income),color='black',binwidth=1)+theme_bw()
```

```{r}
ggplot(a,aes(hr_per_week))+geom_histogram()+theme_bw()
```
```{r}
names(a)[names(a)=='country'] <-'region'
```

```{r}
str(a)
```

```{r}
ggplot(a,aes(region))+geom_bar(aes(fill=income),color='black')+theme_bw()
theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

```{r}
head(a)
```
Train and test

```{r train and test}
library(caTools)
set.seed(101)
sample <- sample.split(a$income,SplitRatio=0.7)
train <-subset(a,sample == T)
test <-subset(a,sample == F)
```


Deploying model

```{r}
model <- glm(income ~. ,family=binomial(logit),data = train)
```

```{r}
summary(model)
```
```{r}
new.step.model <- step(model)

```
```{r}
summary(new.step.model)
```
```{r}
test$predicted.income = predict(model, newdata=test, type="response")

table(test$income, test$predicted.income > 0.5)

```
accuracy of our model
```{r accuracy of the model}
6405+1374/(6405+518+920+1374)

```
recall
```{r recall}
6405/(6405+518)
```
```{r precession}
6405/(6405+920)
```



